Segmentation of Electron Microscopy Images for Connectomics

### 2018-05-02 papers/quals2018/0_introduction.tex
quals:  minor updates to first four sections

One of the critical components of connectomics---the field concerned with reconstructing the wiring diagram of the brain at nanometer resolution---is automatic segmentation of electron microscopy (EM) images.
With recent advancements in EM acquisition techniques, neuroscientists can now generate a terabyte of image data every hour~\cite{richard2016imaging}.
These images are typically anisotropic with $4$nm resolution in the $xy$ plane and \numrange{30}{40}nm between slices. 
At this resolution, we can see the axon terminals and dendritic spines, and the synaptic connections between them.
Neuroscientists hope to further their understanding of the brain's underlying circuitry with accurate reconstructions of every neuron in these volumes and classification of the synaptic connections.

An ambitious manual reconstruction effort in the 1980s resulted in the first complete connectome of any animal, the \textit{Caenorhabditis elegans} worm~\cite{white1986structure}. 
This species has 302 neurons and manual labeling required several years.
More recent studies focus on \textit{Drosophila} flies~\cite{jovanic2016competitive,takemura2015synaptic},  rodents~\cite{richard2016imaging}, and even humans~\cite{sporns2005human}. 
With an EM throughput of one terabyte per hour, neuroscientists can image a cubic millimeter of data (two petabytes) in six months~\cite{suissa2016automatic}. 
At this scale, the manual reconstruction techniques of the 80s are simply infeasible.
Thus, researchers rely on machine learning methods to segment these massive datasets.

Automatic reconstruction produces label volumes that, uncompressed, are much larger in size than the already massive image datasets.
These label volumes assign a 32- or 64-bit integer to every voxel where voxels have the same label only if they belong to the same neuron.
In our paper published in \textit{MICCAI 2017}, we explore the effectiveness of existing general-purpose, image, and video compression techniques on the segmentation datasets.
We find that these existing techniques fail to adequately exploit the typical properties of our label volumes.
Thus, we propose \textit{Compresso}, a new compression algorithm specifically tailored for large label volumes that far exceeds existing strategies.

\begin{figure}
	\includegraphics[width=\linewidth]{./figures/proposal-header.png}
	\caption{From an EM image stack, 3D CNNs generate affinities between voxels (left). These affinities are agglomerated into superpixels which in turn are merged to form a complete segmentation (center). Oftentimes these methods produce errors and thus require error correction to improve the accuracy (right).}
	\label{fig:overview}
\end{figure}

Automatic reconstruction techniques need to be fast, scalable, and accurate.
Ideally, image acquisition is the bottleneck of the connectomics pipeline so reconstruction occurs at a rate of one terabyte per hour~\cite{haehn2017scalable}.
We can achieve this throughput with parallelization among several GPUs with existing techniques~\cite{funke2017deep,parag2017anisotropic}.
However, these automatic methods typically rely on local context for decision making and are agnostic about the underlying biological systems.
Thus, they often make errors at scale and currently require human proofreading or other error correction techniques~\cite{haehn2017guided,error_correction_using_CNN}.

We propose a novel region merging framework that takes as input an oversegmentation of an EM volume (under review, \textit{ECCV 2018}).
Our method imposes both local and global biological constraints onto the output segmentation to more closely match the underlying structure of neuronal processes.
Additionally, our method is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic data without retraining.
Images generated by electron microscopes often differ in appearance because of variations in staining techniques~\cite{briggman2012volume}.
By removing the dependence of our algorithm on the input images, we greatly reduce the need for additional costly ground truth data for each new stack of images.

>>>>

One of the critical components of connectomics---the field concerned with reconstructing the wiring diagram of the brain at nanometer resolution---is automatic segmentation of electron microscopy (EM) images.
With recent advancements in EM acquisition techniques, neuroscientists can now generate a terabyte of image data every hour~\cite{richard2016imaging}.
These images are typically anisotropic with $4$nm resolution in the $xy$ plane and \numrange{30}{40}nm between slices. 
At this resolution, we can see the axon terminals and dendritic spines, and the synaptic connections between them.
Neuroscientists hope to further the understanding of the brain's underlying circuitry with accurate reconstructions of every neuron and classification of every synapse.

An ambitious manual reconstruction effort in the 1980s resulted in the first complete connectome of any animal, the \textit{Caenorhabditis elegans} worm~\cite{white1986structure}. 
This species has 302 neurons and manual labeling required several years.
More recent studies focus on \textit{Drosophila} flies~\cite{jovanic2016competitive,takemura2015synaptic},  rodents~\cite{richard2016imaging}, and even humans~\cite{sporns2005human}. 
With an EM throughput of one terabyte per hour, neuroscientists can image a cubic millimeter of data (two petabytes) in six months~\cite{suissa2016automatic}. 
At this scale, the manual reconstruction techniques of the 80s are infeasible.
Thus, researchers rely on machine learning methods to segment these massive datasets into label volumes (Fig.~\ref{fig:overview}).
These label volumes assign a 32- or 64-bit integer to every voxel where voxels have the same label only if they belong to the same neuron.

Uncompressed, these label volumes are larger in size than the already massive image datasets.
In our paper published in \textit{MICCAI 2017}, we explore the effectiveness of existing general-purpose, image, and video compression techniques on these segmentation datasets~\cite{matejek2017compresso}.
We find that these existing techniques fail to adequately exploit the typical properties of these label volumes.
Thus, we propose \textit{Compresso}, a new compression algorithm specifically tailored for large segmentation datasets, which achieves better compression ratios than all existing methods.

\begin{figure}
	\includegraphics[width=\linewidth]{./figures/proposal-header.png}
	\caption{From an EM image stack, 3D convolutional neural networks generate affinities between voxels (left). A watershed algorithm agglomerates the voxels into supervoxels using these affinities, and these supervoxels are further merged to form a complete segmentation (center). These methods often produce errors and require error correction algorithms to improve the accuracy (right).}
	\label{fig:overview}
\end{figure}

Automatic reconstruction techniques need to be fast, scalable, and accurate.
Ideally, image acquisition is the bottleneck of the connectomics pipeline so reconstruction should occur at a rate of one terabyte per hour~\cite{haehn2017scalable}.
We can achieve this throughput with parallelization among several GPUs with existing techniques~\cite{funke2017deep,parag2017anisotropic}.
However, these automatic methods typically rely on local context for decision making and are agnostic about the underlying biological systems.
Thus, they often make errors at scale and currently require human proofreading or other error correction techniques~\cite{haehn2017guided,error_correction_using_CNN}.

We propose a novel region merging framework that takes as input an oversegmentation of an EM image stack (under review, \textit{ECCV 2018}).
Our method imposes both local and global biological constraints onto the output segmentation to more closely match the underlying structure of neuronal processes.
Additionally, our method is independent of image resolution and acquisition parameters, enabling its application to isotropic and anisotropic datasets without retraining.
Images generated by electron microscopes often differ in appearance because of variations in staining techniques~\cite{briggman2012volume}.
By removing the dependence of our algorithm on the input images, we greatly reduce the need for additional costly ground truth data for each new stack of images.

### 2018-05-02 papers/quals2018/1_compression.tex
quals:  minor updates to first four sections

% !TEX root =  paper.tex
\section{Compression of Label Volumes}

@@

General-purpose compression schemes~\cite{collet2016smaller,deutsch1996zlib,google2016brotli,lehmann2016liblzf,oberhumer2005lzo,pavlov2007lzma,seward1998bzip2,vandevenne2016zopfli,welch1984technique,ziv1978compression} are not optimized for this data.
With Compresso, an algorithm published in MICCAI 2017, we exploit the typical characteristics of label volumes such as large invariant regions without natural relationship between label values. 
These properties render 2D image compression schemes inadequate since they rely on frequency reduction (using e.g., wavelet or discrete cosine transform) and value prediction of pixels based on local context (differential pulse-code modulation)~\cite{roelofs1999png,skodras2001jpeg}. 
Color space optimization strategies in video codecs~\cite{aimar2005x264} also have no effect on label volumes, even though the spatial properties of a segmentation stack (\textit{z}-axis) are similar to the temporal properties of video data (time-axis). 
A compression scheme designed specifically for label volumes is part of the visualization software Neuroglancer~\cite{google2016compressed}. 
This method exploits segmentation homogeneity by creating small blocks with $N$ labels and reducing local entropy to $\log_2{N}$ per pixel. 
Lookup tables then decode the values $[0,N)$ to the original 64-bit labels.

@@

\begin{figure*}[t]
	\begin{center}
		\begin{minipage}{0.45\linewidth}
			\centering
			\includegraphics[width=\linewidth]{./figures/encoding_diagram_opt.pdf}
		\end{minipage}
		\hspace{0.08\linewidth}
		\begin{minipage}{0.45\linewidth}
			\centering
			\includegraphics[width=\linewidth]{./figures/window_values.pdf}
		\end{minipage}
	\end{center}	
	\caption{Compresso works by dividing up the segmentation data into small blocks. On the left we show the intersection of three segments in a $4\times4\times1$ window. We extract a boundary map from this segmentation to transform the window into an integral value between $0$ and $2^{16} - 1$. The location $i$ requires some additional bookkeeping. On the right are the $100$ most common $8 \times 8 \times 1$ windows accounting for $\sim82\%$ of the volume on a representative dataset.}
	\label{fig:compression}
\end{figure*}

Published in MICCAI 2017, we proposed Compresso which is specifically designed for compression of EM label volumes~\cite{matejek2017compresso}.
Compresso works by decoupling the two important components across the image stack: per-segment shape and per-pixel label.
To encode the segment shapes, we consider the boundary pixels between two segments. 
Removing the per-pixel labels, we produce a boundary map for each slice where a pixel $(x, y, z)$ is 1 if either pixel at $(x + 1, y, z)$ or $(x, y + 1, z)$ belongs to a different segment (Fig~\ref{fig:compression}, left). 
The boundary map is divided into non-overlapping congruent 3D windows. If there are $n$ pixels per window, each window $w$ is assigned an integer $V_w \in [0, 2^n)$ where $V_w$ is defined as:

@@

We define $N$ as the number of distinct $V_w$ representing all of the windows in an image stack. 
We construct an invertible function $f(V_w) \to [0, N)$ to transform the window values into a smaller set of integers. 
For all real-world segmentations $N \ll 2^n$; however, we assume no constraint on $N$ in order to guarantee lossless compression. 
With this function, each $V_w$ requires $\log_2{N}$ bits of information to encode. 
This is fewer than the initial number of bits so long as $N \leq 2^{n - 1}$.

So far we have focused exclusively on transforming the boundary map of an image segmentation. 
However, the per-pixel labels themselves are equally important. 
The boundary map divides each image slice into different segments. 
By design, all pixels in the same segment have the same label so we store only one label per segment for each slice. 
We use a connected-component labeling algorithm to store one label per segment \cite{he2009fast}. 
The algorithm labels all pixels clustered within a component $m$ from $M$ section labels.

@@

To decompress the data, we first reconstruct the boundary map from the windows that we extracted.
From there, we can run the same deterministic connected-components algorithm per slice.
We can traverse through the saved labels to fill in all non-boundary labels.
To determine the per-pixel labels for every boundary pixel, we iterate over the entire dataset in raster order. 
Any boundary pixel $(x, y, z)$ with a non-boundary neighbor at $(x - 1, y, z)$ or $(x, y - 1, z)$ shares the same per-pixel label. 
If both relevant neighbors are boundaries (i.e., like pixel $i$ in Fig.~\ref{fig:compression}) we extract the value we had stored.

>>>>

% !TEX root =  paper.tex
\begin{figure*}[t]
	\begin{center}
		\begin{minipage}{0.48\linewidth}
			\centering
			\includegraphics[width=0.9\linewidth]{./figures/encoding_diagram_opt.pdf}
		\end{minipage}
		\begin{minipage}{0.48\linewidth}
			\centering
			\includegraphics[width=0.9\linewidth]{./figures/window_values.pdf}
		\end{minipage}
	\end{center}	
	\caption{Compresso works by dividing up the segmentation data into small blocks. On the left we show the intersection of three segments in a $4\times4\times1$ window. We extract a boundary map from this segmentation to transform the window into an integral value between $0$ and $2^{16} - 1$. This window has an encoded value of 50,978 $(2^1 + 2^5 + 2^8 + 2^9 + 2^{10} + 2^{14} + 2^{15})$. The location $i$ requires some additional bookkeeping. On the right are the $100$ most common $8 \times 8 \times 1$ windows accounting for $\sim82\%$ of the volume on a representative dataset.}
	\label{fig:compression}
\end{figure*}

\section{Compression of Label Volumes}

@@

General-purpose compression schemes~\cite{collet2016smaller,deutsch1996zlib,google2016brotli,lehmann2016liblzf,oberhumer2005lzo,pavlov2007lzma,seward1998bzip2,vandevenne2016zopfli,welch1984technique,ziv1978compression} are not optimized for this data.
These methods do not exploit the typical characteristics of label volumes such as large invariant regions without natural relationship between label values. 
These properties render 2D image compression schemes inadequate since they rely on frequency reduction (using e.g., wavelet or discrete cosine transform) and value prediction of pixels based on local context (differential pulse-code modulation)~\cite{roelofs1999png,skodras2001jpeg}. 
Color space optimization strategies in video codecs~\cite{aimar2005x264} also have no effect on label volumes, even though the spatial properties of a segmentation stack (\textit{z}-axis) are similar to the temporal properties of video data (time-axis). 
A compression scheme designed specifically for label volumes is part of the visualization software Neuroglancer~\cite{google2016compressed}. 
This method exploits segmentation homogeneity by creating small blocks with $N$ labels and reducing local entropy to $\log_2{N}$ per pixel. 
Lookup tables then decode the values $[0,N)$ to the original 64-bit labels.

@@

We propose Compresso, which is specifically designed for compression of EM label volumes~\cite{matejek2017compresso}.
Compresso works by decoupling the two important components across the image stack: per-segment shape and per-pixel label.
To encode the segment shapes, we consider the boundary pixels between two segments. 
Removing the per-pixel labels, we produce a boundary map for each slice where a pixel $(x, y, z)$ is 1 if either pixel at $(x + 1, y, z)$ or $(x, y + 1, z)$ belongs to a different segment (Fig.~\ref{fig:compression}, left). 
The boundary map is divided into non-overlapping congruent 3D windows. If there are $n$ pixels per window, each window $w$ is assigned an integer $V_w \in [0, 2^n)$ where $V_w$ is defined as:

@@

We define $N$ as the number of distinct $V_w$ representing all of the windows in an image stack. 
We construct an invertible function $f(V_w) \to [0, N)$ to transform the window values into a smaller set of integers. 
For all real-world segmentations $N \ll 2^n$; however, we assume no constraint on $N$ in order to guarantee lossless compression. 
With this function, each $V_w$ requires $\log_2{N}$ bits of information to encode. 
This is fewer than the initial number of bits so long as $N \leq 2^{n - 1}$.  
Therefore, when compressing the label volumes, we can store $f(V_w)$ for every window as well as a lookup function for the $N$ unique $f(V_w)$ values to the original integral value.

So far we have focused exclusively on transforming the boundary map of an image segmentation. 
However, the per-pixel labels themselves are equally important. 
The boundary map divides each image slice into different segments. 
By design, all pixels in the same segment have the same label so we store only one label per segment for each slice. 
We use a connected-component labeling algorithm to identify each component and store one label per segment \cite{he2009fast}.

@@

To decompress the data, we first reconstruct the boundary map from the windows that we extracted.
From there, we can run the same deterministic connected-components algorithm per slice.
We can traverse through the saved labels to fill in all non-boundary labels.
To determine the per-pixel labels for every boundary pixel, we iterate over the entire dataset in raster order. 
Any boundary pixel $(x, y, z)$ with a non-boundary neighbor at $(x - 1, y, z)$ or $(x, y - 1, z)$ shares the same per-pixel label. 
If both relevant neighbors are boundaries (i.e., like pixel $i$ in Fig.~\ref{fig:compression}) we extract the value we previously stored.

### 2018-05-02 papers/quals2018/2_error_correction.tex
quals:  minor updates to first four sections

Automatic reconstruction methods need to be fast enough to scale to petabyte datasets while still maintaining a high-level of accuracy.
The most accurate methods, like flood-filling networks~\cite{januszewski2016flood}, are too slow to scale. 
Unfortunately, methods that can scale to petabyte datasets typically rely on only local context and can produce errors at scale~\cite{haehn2017scalable}. 
Therefore, it is necessary to employ error correction strategies on the segmentations from current reconstruction pipelines.
We propose a biologically-constrained region merging algorithm to correct \textit{split errors} in the initial segmentation.

@@

Additional research builds on top of these region-based methods to correct errors in the segmentation. 
These input segmentations can contain two types of errors.
In a \textit{split error}, one neurons contains multiple labels.
In a \textit{merge error}, two or more neurons receive the same label.
This can be done either using human proofreading~\cite{haehn2017guided,haehn2014design,mojo2} or automatically~\cite{rolnick2017morphological,error_correction_using_CNN}. 
In both cases, available methods are pixel-based and do not include global biological constraints into the decision making process. 
Our method can take as input any existing segmentation pipeline.

@@

\subsubsection{Skeleton-Based Graph Generation}
\label{sec:skeletonization}
Most region merging methods create a region graph by removing small-sized segments and linking each pair of adjacent segments, which can still lead to a large graph size due to the irregular shape of neural structures.
We use a skeleton representation of the segmentation to reduce the graph size with geometric constraints on the connectivity of two adjacent segments to prune edges.

@@

\begin{figure}[t]
	\centering
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error1.png}		
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error2.png}				
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error3.png}
	\end{minipage}
	\caption{Three erroneously split segments.}
	\label{fig:merge_candidates}
\end{figure}
\subsubsection{Optimization-Based Graph Partition}

@@

We need to convert the probabilities into the following weighting scheme to solve the multicut problem with the greedy-edge heuristic~\cite{andres2011probabilistic,keuper2015efficient}.
Given the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e$ is defined as
%p_e &=\mbox{CNN}(x_1, x_2) \\
\begin{align}
w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}},
\end{align}
where $\beta$ is a tunable parameter that encourages over- or under-segmentation. 
Since, there are many more lifted edges than adjacent edges, we scale down the lifted weights proportionally to their total number  
~\cite{beier2017multicut}.

@@

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-Kasthuri-Luigi-Test.pdf}
	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--1.pdf}
	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--2.pdf}
	\caption{Segmentation benchmark results on three volumes. We compare our method (red) to the baseline segmentation (green) and an oracle (blue) that optimally partitions our constructed graph from our method. Lower VI scores are better. Our method improves the segmentation accuracy over the baseline in all cases.
		Note that our model is only trained on the Kasthuri training volume and it generalizes well to the FlyEM dataset.}
	\label{fig:variation-of-information}
\end{figure*}

@@

For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we apply a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication. 
This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize under-segmentation error. 
The algorithm first computes multi-channel 3D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
The membrane prediction channel is used to produce an oversegmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
We used exactly the same parameters as the publicly available code for this algorithm.
\\~\\
\noindent\textbf{Graph Generation.}
The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. 
Ideally, our graph will have an edge for every over-segmented pair of labels with few edges between correctly segmented pairs. 
After considering various thresholds, we find that $t_{low} = \SI{210}{\nano\meter}$ and $t_{high} = \SI{300}{\nano\meter}$ produce expressive graphs with a scalable number of nodes and edges.
During implementation, we use nanometers instead of voxels for these thresholds to have uniform units across all datasets.
\\~\\
\noindent\textbf{Edge Weight Learning.}
\label{sec:network-parameters}
We use half of the Kasthuri dataset for training and validation. 
We train on 80\% of the potential merge candidates for this volume.
We validate the CNN classifier on the remaining 20\% of the candidates. 
Since our input does not require the image data, we can train on the anisotropic Kasthuri data and test on the isotropic FlyEM data.
\\~\\
\noindent\textbf{Training Augmentation.}
Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that train on a unique window for each voxel. 
The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields 640 positive merge examples and 4821 negative ones.
To avoid overfitting our deep networks, we apply the following augmentations on the training examples.
During a single batch, we randomly select ten positive and ten negative examples. 
With probability 0.5, an example is reflected across the $xy$-plane. 
We then rotate each example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
The supplemental material contains experiments demonstrating the benefits of this augmentation strategy.
We have 20,000 such examples per epoch.

\subsubsection{Error Metrics}
\label{sec:variation-of-information}
We evaluate the performance of the different methods using the split variation of information (VI)~\cite{meila2003comparing}.
Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$, over- and under-segmentation are quantified by the conditional entropies $H(GT | SG)$ and $H(SG | GT)$, respectively. 
Since we are measuring the entropy between two clusterings, lower VI scores are better.
The sum of these conditional entropies gives the total variation of information.

@@

@@

@@

\noindent\textbf{Graph Generation.}
Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the algorithm discussed in Sec.~\ref{sec:skeletonization}. 
This edge pruning is essential for the graph partitioning algorithm, which has a non-linear computational complexity dependence on the number of edges. 
The baseline algorithm considers all adjacent regions for merging. 
Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., 764 compared to 974). 
Our pruning heuristic removes at least $3.5\times$ the number of edges on all datasets, achieving a maximum removal rate of $4.15\times$.
However, there are some adjacent over-segmented labels which are not considered.

We generate edges in our graph by using information from the skeletons. 
In particular, we do not enforce the constraint that edges in our graph correspond to adjacent segments.
Although neurons are continuous, the EM images often have noisy spots which cause an interruption in the input segmentation.
We still want to reconstruct these neurons despite the fact that the initial segmentation is non-continuous. 
The second and fourth examples in Fig.~\ref{fig:qualitative-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
\\~\\
\noindent\textbf{Failure Cases}
There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons.
Fig.~\ref{fig:skeleton-results} shows two such cases with the closest endpoints circled. 
In the right example the small segment is carved from the larger segment in a location where there are no skeleton endpoints. 
There are on average 177 such examples in our datasets.
\\~\\
\noindent\textbf{Edge Weight Learning}
%\subsubsection{Inference Augmentation}
%\noindent\textbf{Inference Augmentation.}
Data augmentation at test time can improve accuracy results~\cite{lee2017superhuman,zeng2017deepem3d}.
When computing the probability to merge two segments, we randomly rotate and flip the examples three times (in the same fashion as training augmentation).
Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all test datasets.
As shown by the ROC curve, the test results on the FlyEM data are better than the results for Kasthuri.
In part this comes from the disparity in the number of positive to negative merge candidates in the two graphs. 
The network easily classifies most of the negative examples leaving only a few difficult examples to predict.
Since there are more negative examples in relation to the positive examples in the FlyEM data, the ROC curve is greater.

>>>>

Automatic reconstruction methods need to be fast enough to scale to petabyte datasets while still maintaining a high-level of accuracy.
The most accurate methods, like flood-filling networks~\cite{januszewski2016flood}, are currently far too slow.
Unfortunately, methods that can scale to petabyte datasets typically rely on only local context and can produce errors at scale~\cite{haehn2017scalable}. 
Therefore, it is necessary to employ error correction strategies on the segmentations from current reconstruction pipelines.
We propose a biologically-constrained region merging algorithm to correct \textit{split errors} in the initial segmentation.

@@

Additional research builds on top of these region-based methods to correct errors in the segmentation. 
These input segmentations can contain two types of errors.
In a \textit{split error}, one neuron contains multiple labels.
In a \textit{merge error}, two or more neurons receive the same label.
This can be done either using human proofreading~\cite{haehn2017guided,haehn2014design,mojo2} or automatically~\cite{rolnick2017morphological,error_correction_using_CNN}. 
In both cases, available methods are pixel-based and do not include global biological constraints into the decision making process. 
Our method can take as input any existing segmentation pipeline.

@@

\subsubsection{Skeleton-Based Graph Generation}
\label{sec:skeletonization}

Most region merging methods create a region graph by removing small-sized segments and linking each pair of adjacent segments, which can still lead to a large graph size due to the irregular shape of neural structures.
We use a skeleton representation of the segmentation to reduce the graph size with geometric constraints on the connectivity of two adjacent segments to prune edges.

@@

\subsubsection{Optimization-Based Graph Partition}

@@

We need to convert the probabilities into the following weighting scheme to solve the multicut problem with the greedy-edge heuristic~\cite{andres2011probabilistic,keuper2015efficient}.
Given the probability that the nodes belong to the same neuron is $p_e$, the edge weight $w_e$ is defined as
%p_e &=\mbox{CNN}(x_1, x_2) \\
\begin{align}
w_e = \log{\frac{p_e}{1 - p_e}} + \log{\frac{1 - \beta}{\beta}},
\end{align}
where $\beta$ is a tunable parameter that encourages over or undersegmentation. 
Since, there are many more lifted edges than adjacent edges, we scale down the lifted weights proportionally to their total number  
~\cite{beier2017multicut}.

@@

\begin{figure}[t]
	\centering
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error1.png}		
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error2.png}				
	\end{minipage}
	\hfill
	\begin{minipage}{0.32\linewidth}
		\includegraphics[width=\linewidth]{./figures/split_error3.png}
	\end{minipage}
	\caption{Three erroneously split segments. In each instance, the skeletons for each segment have nearby endpoints indicating a split error.}
	\label{fig:merge_candidates}
\end{figure}

@@

For the FlyEM data, based on the authors' suggestion~\cite{takemura2017connectome}, we apply a context-aware delayed agglomeration algorithm~\cite{10.1371/journal.pone.0125825} that shows improved performance on this dataset over the pipeline used in the original publication. 
This segmentation framework learns voxel and supervoxel classifiers with an emphasis to minimize undersegmentation error. 
The algorithm first computes multi-channel 3D predictions for membranes, cell interiors, and mitochondria, among other cell features. 
The membrane prediction channel is used to produce an oversegmented volume using 3D watershed, which is then agglomerated hierarchically up to a certain confidence threshold. 
We used exactly the same parameters as the publicly available code for this algorithm.
\\~\\
\noindent\textbf{Graph Generation.}
The two parameters for the graph pruning algorithm (Sec.~\ref{sec:skeletonization}) are $t_{low}$ and $t_{high}$. 
Ideally, our graph will have an edge for every oversegmented pair of labels with few edges between correctly segmented pairs. 
After considering various thresholds, we find that $t_{low} = \SI{210}{\nano\meter}$ and $t_{high} = \SI{300}{\nano\meter}$ produce expressive graphs with a scalable number of nodes and edges.
During implementation, we use nanometers instead of voxels to standardize units across all datasets.
\\~\\
\noindent\textbf{Edge Weight Learning.}
\label{sec:network-parameters}
We use half of the Kasthuri dataset for training and validation. 
We train on 80\% of the potential merge candidates for this volume.
We validate the CNN classifier on the remaining 20\% of the candidates. 
Since our input does not require the image data, we can train on the anisotropic Kasthuri data and test on the isotropic FlyEM data.

\noindent\textbf{Training Augmentation.}
Since our input is an existing segmentation of the EM images, there are very few training examples compared to per-pixel classifiers that train on a unique window for each voxel. 
The Kasthuri dataset represents a region of brain over $\SI[product-units=single]{800}{\micro\meter}^3$ in volume and only yields 640 positive merge examples and 4821 negative ones.
To avoid overfitting our deep networks, we apply the following augmentations on the training examples.
During a single batch, we randomly select ten positive and ten negative examples. 
With probability 0.5, an example is reflected across the $xy$-plane. 
We then rotate each example by a random angle between $0$ and $360$ degrees using nearest neighbor interpolation. 
We have 20,000 such examples per epoch.

\subsubsection{Error Metrics}
\label{sec:variation-of-information}
We evaluate the performance of the different methods using the split variation of information (VI) score~\cite{meila2003comparing}.
Given a ground truth labeling $GT$ and our automatically reconstructed segmentation $SG$, over and undersegmentation are quantified by the conditional entropies $H(GT | SG)$ and $H(SG | GT)$, respectively. 
Since we are measuring the entropy between two clusterings, lower VI scores are better.
The sum of these conditional entropies gives the total variation of information.

@@

\begin{figure*}[t!]
	\centering
	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-Kasthuri-Luigi-Test.pdf}
	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--1.pdf}
	\includegraphics[width=0.32\linewidth]{./figures/benchmark/voi-FlyEM-Vol--2.pdf}
	\caption{Segmentation benchmark results on three volumes. We compare our method (red) to the baseline segmentation (green) and an oracle (blue) that optimally partitions our constructed graph from our method. Lower VI scores are better. Our method improves the segmentation accuracy over the baseline in all cases.
		Note that our model is only trained on the Kasthuri training volume and it generalizes well to the FlyEM datasets.}
	\label{fig:variation-of-information}
\end{figure*}

@@

\noindent\textbf{Graph Generation.}
Table \ref{table:skeletonization} shows the results of pruning the skeleton graph using the algorithm discussed in Sec.~\ref{sec:skeletonization}. 
This edge pruning is essential for the graph partitioning algorithm, which has a non-linear computational complexity dependence on the number of edges. 
The baseline algorithm considers all adjacent regions for merging. 
Our method removes a significant portion of these candidates while maintaining a large number of the true merge locations (e.g., 764 compared to 974). 
Our pruning heuristic removes at least $3.5\times$ the number of edges on all datasets, achieving a maximum removal rate of $4.15\times$.
However, there are some adjacent oversegmented labels which are not considered.

@@

We generate edges in our graph by using information from the skeletons. 
In particular, we do not enforce the constraint that edges in our graph correspond to adjacent segments.
Although neurons are continuous, the EM images often have noisy spots which cause an interruption in the input segmentation.
We still want to reconstruct these neurons despite the fact that the initial segmentation is non-continuous. 
The second and fourth examples in Fig.~\ref{fig:qualitative-results} show correctly reconstructed neurons where two of the segments are non-adjacent. 
\\~\\
\noindent\textbf{Failure Cases.}
There are some pairs of segments which we do not consider for merging because of our reliance on the skeletons.
Fig.~\ref{fig:skeleton-results}, top, shows two such cases with the closest endpoints circled. 
In the right example the small segment is carved from the larger segment in a location where there are no skeleton endpoints. 
There are on average 177 such examples in our datasets.
\\~\\
\noindent\textbf{Edge Weight Learning.}
Fig.~\ref{fig:receiver-operating-characteristic} shows the receiver operating characteristic (ROC) curve of our CNN classifier for all test datasets.
As shown by the ROC curve, the test results on the FlyEM data are better than the results for Kasthuri.
In part this comes from the disparity in the number of positive to negative merge candidates in the two graphs. 
The network easily classifies most of the negative examples leaving only a few difficult examples to predict.
Since there are more negative examples in relation to the positive examples in the FlyEM data, the ROC curve is greater.
